PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-05-15 paper/ms.tex
paper: fix typos

We wish \ptfob\ were a planet. It would be quite exceptional. It would
be the youngest known hot Jupiter \citep{van_eyken_ptf_2012}, orbiting
a T Tauri star in the Orion-OB1a cluster.  It would have the shortest
orbital period of any hot Jupiter.  With such a short period, it would
probably be filling its Roche lobe, and actively losing mass to its
host star.  Not only that, but the rapidly-rotating host star is
probably oblate enough to torque the planet's orbit into and out of
the transiting configuration on a time scale of years
\citep{barnes_measurement_2013,ciardi_followup_2015,kamiaka_revisiting_2015}.

>>>>

We wish \ptfob\ were a planet. It would be quite exceptional. It would
be the youngest known hot Jupiter \citep{van_eyken_ptf_2012}, orbiting
a T Tauri star in the Orion-OB1a cluster.  It would have the shortest
orbital period of any hot Jupiter.  With such a short period, it would
probably be filling its Roche lobe, and actively losing mass to its
host star.  Not only that, but the rapidly-rotating host star is
probably oblate enough to torque the planet's orbit into and out of
the transiting configuration on a timescale of years
\citep{barnes_measurement_2013,ciardi_followup_2015,kamiaka_revisiting_2015}.
